### 2018-04-06 Sections/economics_of_the_quantum_internet.tex
time-sharing

@@

In Secs.~\ref{sec:quant_ec_lev} \& \ref{sec:GVQC} we argue that because of the super-linear scaling in the computational power of networked quantum computers, it will be most economically efficient to unify the world's entire collective quantum computational resources over the network and time-share their joint computational power. For this reason, we will assume that global quantum computing resources are unified, and time-shared equitably (as described in Sec.~\ref{sec:arb_free_time_share}), overseen by a trusted central authority, congruent with our efficient market assumptions (Sec.~\ref{sec:eff_markets}).

@@

In the context of our global network of unified quantum computers, how do we fairly and equitably allocate time-shares between contributors? We now derive an elementary arbitrage-free model for equitable time-sharing in such a network.

>>>>

%
% Time-Sharing
%

\subsection{Time-sharing}\label{sec:time_share}\index{Time-sharing}

Suppose we have a classical network comprising two computers with equal processing power, one held by Alice and the other by Bob. One could network these computers into a cluster to create a more powerful virtual computer of approximately twice the power of the individual computers. When utilising them, one option is for Alice and Bob to each use their individual computers in isolation for a given duration. The other  is for them to cluster them and agree to time-share the virtual computer, each using the cluster for half the time. Which is the better outcome for Alice and Bob?

In the case of classical computing there is clearly no difference between using the computers in isolation or networking them and time-sharing their joint compute power -- one either uses a computer twice as powerful for half the amount of time, or half as powerful for twice the amount of time.

For quantum computers this is no longer the case, since the computational power of quantum computers in general grows super-linearly with the number of qubits. That is, the joint computational power of unified quantum computers is more than the sum of the parts.

Therefore, in the quantum context it makes more sense to unify computational assets into a larger virtual computer and time-share its joint computational power than to utilise the assets in isolation.

For this reason, henceforth we will assume an environment in which owners of quantum hardware network and unify their computational power, sharing the virtual computer's power between them.

In Sec.~\ref{sec:arb_free_time_share} we present an explicit model for equitable time-sharing, which is optimal from a market perspective.

@@

In Sec.~\ref{sec:time_share} we argue that because of the super-linear scaling in the computational power of networked quantum computers, it will be most economically efficient to unify the world's entire collective quantum computational resources over the network and time-share their joint computational power. For this reason, we will assume that global quantum computing resources are unified, and time-shared equitably (as described in Sec.~\ref{sec:arb_free_time_share}), overseen by a trusted central authority, congruent with our efficient market assumptions (Sec.~\ref{sec:eff_markets}).

@@

In the context of our time-shared global network of unified quantum computers (Sec.~\ref{sec:time_share}), how do we fairly and equitably allocate time-shares between contributors? We now derive an elementary arbitrage-free model for equitable time-sharing in such a network.
